---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ifwtrends

<!-- badges: start -->
<!-- badges: end -->

ifwtrends is used to evaluate Google Trends data for economic 
forecasts.

## Installation

You can install the current development version of
ifwtrends from [GitHub](https://github.com/johannes97s/ifwtrends) with:

``` r
# install.packages("devtools")
devtools::install_github("johannes97s/ifwtrends", build_vignettes = TRUE)
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ifwtrends)
# Search keywords and do a subsequent PC analysis on a
# GTrends time series 
pca(keywords = c("Pluto", "Saturn"),
    categories = 0,
    geo = "DE",
    start = "2006-01-01",
    end = Sys.Date(),
    components = max(length(keywords), length(categories)))

# Search for a GTrends category and do a subsequent PC
# analysis
pca(keywords = NA,
    categories = c(651),
    geo = "DE",
    start = "2006-01-01",
    end = Sys.Date(),
    components = max(length(keywords), length(categories)))

```

## Roadmap

| Function | Description | Status |
|---|---|---|
| `daily_series()` | Uses a complex econometric method to calculate daily data based on monthly data. | 游릭 Implemented |
| `est_trends()` | Estimates the trend of a Google Trends category. | 游릭 Implemented |
| `factorR2()` | Calculates and plots the $R^2$ of the time series. | 游릭 Implemented |
| `roll()` | A function to use `pca()` on backtesting. | 游릭 Implemented |
| `pca()` | A function to do a Principal Component Analysis on GTrends data. | 游릭 Implemented |
